Reviewer Comments (Scientific Reports)

### 2020-03-28 notebook/sci_rep_reviews.Rmd
Add a line of text prior to getting into reviewer responses

---
title: "Reviewer Comments (Scientific Reports)"
author: "Brad Duthie"
date: "30 December 2019"
output:
  pdf_document: default
  html_document: default
---

>>>>

---
title: "Reviewer Comments (Scientific Reports)"
author: "Brad Duthie"
output:
  pdf_document: default
  html_document: default
---

**I am grateful for the helpful comments of reviewers on a previous version of this manuscript. I respond to these comments point by point below.**
